Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-20 prop_iop.tex
prop_iop.tex \subsection{Increase the Measurement Resource} Updating...

We can apply the idea of restricting the event space in example~\ref{ex:three-dimensional-three-value},
but instead of commuting sub-event space, we will try to find some
subset~$\events'\subseteq\events$ such that $\bar{\mu}|_{\events'}$
has an non-empty core. The following are three of all possibilities:
\begin{itemize}
\item When $\events'=\events\backslash\left\{ \proj{\ps'}\right\} $, because
$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} $.
\item When $\events'=\events\backslash\left\{ \proj{\ps}\right\} $, because
$\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we have $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{1}}^{B}\right\} $.
\item When $\events'=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
we have $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$
as well as $\mu_{\ket{2}}^{B}$ and $\mu_{\ket{1}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events'}\right)$.
\end{itemize}
Each of these possibilities is compatible with some but not all of
the observations. The first two possibilities are particular interesting
since each two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}\right\} $
in the Hilbert space of dimension 3, where the cross product of complex
vectors is defined in definition~\ref{def:cross-product}.

As we illustrated in figure~\ref{fig:three-dimensional-3-value},
if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
is contained in a plane, which contains no area in the sphere. On
the other hand, if the states mapping to $\imposs$ contain some area
in the sphere as in figure~\ref{fig:three-dimensional-3-value-1},
each plane intersecting the area suggests different pure state inducing
$\bar{\mu}$. However, these suggestions contradict with each others,
which implies $\bar{\mu}$ has an empty core. Furthermore, the larger
the area, the more state vectors which are inconsistent with any particular
Born rule probability measure. Therefore, the area of the 1-dimensional
projectors mapping to $\imposs$ could indicate how much $\bar{\mu}$
deviate from the Born rule probability measures. 
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figure3} 
\par\end{centering}
\caption{\label{fig:three-dimensional-3-value-1}Plotted in $\mathbb{R}^{3}$,
assume the 1-dimensional projectors whose latitude is higher than
the green circle maps to $\imposs$ by $\bar{\mu}$, for example $\bar{\mu}\left(\proj{0'}\right)=\bar{\mu}\left(\proj{2'}\right)=\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$.
Since $\ket{0'}$ and $\ket{2'}$ are in a plane, $\bar{\mu}$ might
be induced by its normal vector~$\ket{1'}$. Also, since $\ket{0'}$
and $\ket{\bar{2}}$ are in a plane, $\bar{\mu}$ might be induced
by its normal vector~$\ket{\bar{1}}$. However, $\mu_{\ket{1'}}^{B}$
is inconsistent with $\bar{\mu}\left(\proj{\bar{2}}\right)=\imposs$,
and $\mu_{\ket{\bar{1}}}^{B}$ is inconsistent with $\bar{\mu}\left(\proj{2'}\right)=\imposs$.
Therefore, $\bar{\mu}$ has an empty-core.}
\end{figure}

In this sense, we found that the area of the 1-dimensional projectors
mapping to $\imposs$ depends on the maximal length of the intervals,
which represents the ability of measurement equipment. In particular,
we have the following results whose details are described in appendix~\ref{sec:Real-Interval-valued-Frame}.
\begin{itemize}
\item The radius of any disk inside the area of the 1-dimensional projectors
mapping to $\imposs$ must smaller than $\pi / 4$ (theorem~\ref{thm:pi-div-4}).
\item When the radius of any disk inside the area of the 1-dimensional projectors
mapping to $\imposs$ between $\arcsin\left(1 / \sqrt{3}\right)$
and $\pi / 4$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
(theorem~\ref{thm:arcsin-one-over-sqrt-three}).
\item When the radius of any disk inside the area of the 1-dimensional projectors
mapping to $\imposs$ between $\pi/6$ and $\arcsin\left(1 / \sqrt{3}\right)$,
we have $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=\frac{1}{3}$
(to be typed...).
\end{itemize}
In general, we conjecture that if the measurement equipment is made
more and more precise, the corresponding interval-valued probability
measure will be closer and closer to the Born rule. In the limit case,
$\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$ we do
indeed recover the conventional Gleason's theorem and the Born rule.

@@

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\pi / 2\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi / 2-\theta_{0},\pi / 2\right]\right)$.\end{lemma}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figureb1.eps} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
\begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by theorem~\ref{thm:interval-valued-frame-function}, we have

>>>>

This section extend the idea of restricting the event space, but instead
of commuting sub-event space, we will try to find some subset~$\events'\subseteq\events$
such that $\bar{\mu}|_{\events'}$ has an non-empty core. This could
help us understand the core because of the following identity
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\label{eq:core-intersection}
\end{equation}
if we know more about the right-hand side of the equation, we can
have more idea about the left-hand side. This idea can be applied
to example~\ref{ex:three-dimensional-three-value}, and the following
are three of all possibilities:
\begin{itemize}
\item When $\events_{1}=\events\backslash\left\{ \proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\imposs$, we have
$\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} $.
\item When $\events_{2}=\events\backslash\left\{ \proj{\ps}\right\} $,
because $\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps'})=\imposs$, we
have $\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{1}}^{B}\right\} $.
\item When $\events_{3}=\events\backslash\left\{ \proj{0},\proj{\ps},\proj{\ps'}\right\} $,
because $\bar{\mu}(\proj{\phi})\ne\necess$ for all $\ket{\phi}$,
we have $\mu_{\frac{\mathbb{1}}{3}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$
as well as $\mu_{\ket{2}}^{B}$ and $\mu_{\ket{1}}^{B}\in\mathrm{core}\left(\bar{\mu}|_{\events_{3}}\right)$.
\end{itemize}
Each of these possibilities is compatible with some but not all of
the observations. In another word, 
\begin{equation}
\mathrm{core}\left(\bar{\mu}\right)=\bigcap_{\events'\subseteq\events}\mathrm{core}\left(\bar{\mu}|_{\events'}\right)\subseteq\mathrm{core}\left(\bar{\mu}|_{\events_{1}}\right)\cap\mathrm{core}\left(\bar{\mu}|_{\events_{2}}\right)=\left\{ \mu_{\ket{2}}^{B}\right\} \cap\left\{ \mu_{\ket{1}}^{B}\right\} =\emptyset\textrm{ .}
\end{equation}
The first two possibilities are particular interesting since each
two 1-dimensional projectors~$\proj{\psi_{0}}$ and $\proj{\psi_{1}}$
mapped to $\imposs$ suggests there is a subset~$\events'\subseteq\events$
such that $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi_{0}}\times\ket{\psi_{1}}}^{B}\right\} $
in the Hilbert space of dimension 3, where the cross product of complex
vectors is defined in definition~\ref{def:cross-product}.

As we illustrated in figure~\ref{fig:three-dimensional-3-value},
if $\bar{\mu}$ has a non-empty core, the states mapping to $\imposs$
is contained in a plane, which contains no area in the sphere. On
the other hand, if the states mapping to $\imposs$ contain some area
in the sphere as in figure~\ref{fig:three-dimensional-real-frame-1},
and this area intersects a plane~$\events'$, then $\mathrm{core}\left(\bar{\mu}|_{\events'}\right)=\left\{ \mu_{\ket{\psi}}^{B}\right\} $,
where $\ket{\psi}$ is the normal vector of $\events'$. Since different
planes have different normal vectors, $\bar{\mu}$ has an empty core.
Furthermore, the larger the area, the more state vectors which are
inconsistent with any particular Born rule probability measure. In
another word, there are more different singleton sets in the right-hand
side of equation~(\ref{eq:core-intersection}). Therefore, the area
of the 1-dimensional projectors mapping to $\imposs$ could indicate
how much $\bar{\mu}$ deviate from the Born rule probability measures.

In this sense, we found that the area of the 1-dimensional projectors
mapping to $\imposs$ depends on the maximal length of the intervals,
which represents the ability of measurement equipment. In particular,
we have the following results whose details are described in \ref{sec:Real-Interval-valued-Frame}. 
\begin{itemize}
\item The radius of any disk inside the area of the 1-dimensional projectors
mapping to $\imposs$ must smaller than $\pi / 4$ (theorem~\ref{thm:pi-div-4}).
\item When the radius of any disk inside the area of the 1-dimensional projectors
mapping to $\imposs$ between $\arcsin\left(1 / \sqrt{3}\right)$
and $\pi / 4$, we have $\unknown\in\mathscr{I}$, i.e., $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=1$
(theorem~\ref{thm:arcsin-one-over-sqrt-three}).
\item When the radius of any disk inside the area of the 1-dimensional projectors
mapping to $\imposs$ between $\pi/6$ and $\arcsin\left(1 / \sqrt{3}\right)$,
we have $\underset{\left[l,r\right]\in\mathscr{I}}{\max}r-l=\frac{1}{3}$
(to be typed...).
\end{itemize}
In general, we conjecture that if the measurement equipment is made
more and more precise, the corresponding interval-valued probability
measure will be closer and closer to the Born rule. In the limit case,
$\mathscr{I}=\set{\left\{ a\right\} }{a\in\left[0,1\right]}$ we do
indeed recover the conventional Gleason's theorem and the Born rule.

@@

\begin{lemma}\label{lemma:imposs-imply-same-value}Given
$\theta_{0}\in\left[0,\pi/2\right]$ and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\pi/2-\theta_{0},\pi/2\right]\right)$.\end{lemma}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{figureb1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}, where every
vector above the light green circle maps to $\imposs$, and we want
to prove that every vector between dark green and light blue maps
to the same interval.}
\end{figure}
\begin{proof} We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by theorem~\ref{thm:interval-valued-frame-function}, we have
